Yeast RNA-seq 48 sample simulation study: Bimodal alternative, 2000 DE genes

### 2018-09-14 datasets/RNA-Seq/yeast-simulation-bimodalalternative-highpi0.Rmd
Edit section headers
Standardize random seeds ffor different covariate settings

# Non-null Comparisons with Strongly Informative Covariate

@@

```
# Non-null Comparisons with Weakly Informative Covariate

@@

```{r d5-uw, results='hide', message=FALSE}
rseed <- 445
sampleSize <- 5
nDE <- 500

@@

```{r d10-uw, results='hide', message=FALSE}
rseed <- 868
sampleSize <- 10
nDE <- 500

>>>>

@@

# Non-null Comparisons with Weakly Informative Covariate

@@

```{r d5-uw, results='hide', message=FALSE}
rseed <- 198
sampleSize <- 5
nDE <- 500

@@

```{r d10-uw, results='hide', message=FALSE}
rseed <- 961
sampleSize <- 10
nDE <- 500

### 2018-09-14 datasets/RNA-Seq/yeast-simulation-bimodalalternative.Rmd
Edit section headers
Standardize random seeds ffor different covariate settings

@@

```{r d5-uw, results='hide', message=FALSE}
rseed <- 445
sampleSize <- 5
nDE <- 2000

@@

```{r d10-uw, results='hide', message=FALSE}
rseed <- 868
sampleSize <- 10
nDE <- 2000

>>>>

# Non-null Comparisons with Weakly Informative Covariate

@@

```{r d5-uw, results='hide', message=FALSE}
rseed <- 198
sampleSize <- 5
nDE <- 2000

@@

```{r d10-uw, results='hide', message=FALSE}
rseed <- 961
sampleSize <- 10
nDE <- 2000
